Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-18 src/article.tex
urls

Some items among the Tagliavini collection are no longer in a playing
condition or are too fragile to continue to be available by museum
visitors. One of those fragile instruments is a 1547 Harpsichord in the
italian style by Alessandro Trasuntino
\cite{Wraight2024}\footnote{examples of similar instruments by
Trasuntino available online in the [Royal College of Music Collection
(1531)](https://museumcollections.rcm.ac.uk/collection/Details/collect/58) and
the [Musée de la musique collection
(1538)](https://carmentis.kmkg-mrah.be:443/eMP/eMuseumPlus?service=ExternalInterface&module=collection&objectId=106088&viewType=detailView)
}, which was used as the basis for an interactive exhibition commisioned
by San Colombano.

@@

This is particularly pertinent as it relates to conservation of musical
instruments, as they represent both historic objects, but also tools for
creating music. Historical musical instruments present an interesting
problem for cultural heritage as they are both a physical object but
also a tool for making music. This begs the question, can we use haptics
to preserve experiences of the past? The proposed project intends to
develop further the methodologies implemented in musical haptics
projects \cite{MusicalHaptics} such as \cite{Timmermans2020}.

@@

Museum staff want visitors to be engaged but limits in staffing and
funding limit how vistors can interact with collections
\cite{Templeton2018,
McAlpine2014}. For musical instrument museums there is an additional
difficulty in the balance of keeping historical instruments playable
\cite{McAlpine2013}. The fragility and decay of musical instruments
means that there is an inveitable point where instruments will no longer
be in a playable condition \cite{McAlpine2014, Fritz2017}

>>>>

Some items among the Tagliavini collection are no longer in a playing
condition or are too fragile to continue to be available by museum
visitors. One of those fragile instruments is a 1547 Harpsichord in the
italian style by Alessandro Trasuntino
\cite{Wraight2024}\footnote{examples of similar instruments by
Trasuntino available online in the Royal College of Music Collection
(1531: \url{https://museumcollections.rcm.ac.uk/collection/Details/collect/58}) and
the Musée de la musique collection
(1538: \url{https://carmentis.kmkg-mrah.be:443/eMP/eMuseumPlus?service=ExternalInterface&module=collection&objectId=106088&viewType=detailView})
}, which was used as the basis for an interactive exhibition commisioned
by San Colombano.

@@

This is particularly pertinent as it relates to conservation of musical
instruments, as they represent both historic objects, but also tools for
creating music. Historical musical instruments present an interesting
problem for cultural heritage as they are both a physical object but
also a tool for making music. This begs the question, can we use haptics
to preserve experiences of the past? The proposed project intends to
develop further the methodologies implemented in musical haptics
projects \cite{MusicalHaptics2018} such as \cite{Timmermans2020}.

@@

Museum staff want visitors to be engaged but limits in staffing and
funding limit how vistors can interact with collections
\cite{Templeton2018,
McAlpine2014}. For musical instrument museums there is an additional
difficulty in the balance of keeping historical instruments playable
\cite{McAlpine2014}. The fragility and decay of musical instruments
means that there is an inveitable point where instruments will no longer
be in a playable condition \cite{McAlpine2014, Fritz2017}
